Why there are more species in several small patches vs few large patches:

### 2024-02-26 ms_SLOSS.Rmd
Ms corrections

For the simulations made with random block habitat patterns, the patches do not have the same sizes but there is a distribution with a minimum size determined by the patch-size parameter and a bigger maximum size (Figures S9 - S11). The pattern is similar to the regular case,  with a maximum richness for intermediate patch sizes and values of $\lambda$ higher than 2 the maximum is at the lower habitat patch size (Figure S1 & S2). The sizes of patches for the random block simulations are bigger so species richness and diversity are lower, except for the minimum patch size (Figure S7 & S8). Examples of simulations with random block and regular habitat patterns are shown in the supplementary material (Figures S9 & S32). In these figures, we can observe that for the minimum patch size only migrants survive for regular habitat patterns with neutral and hierarchical models.

@@

In previous simulation studies, it was shown that fragmentation was important when the habitat amount is low, around 10% [@Hanski2015; @Rybicki2013], but it has been observed that with habitat levels around 10-20% the effect of fragmentation is positive or have an intermediate maximum [@Loke2019; @With2016], and with lower habitat amount (e.g 7%) the arrangement of patches does not matters, we obtained similar patterns with 40% habitat amount, which is near the amount used in newer simulated studies (32%) that also obtain more species richness with more fragmentation [@Rybicki2020].

>>>>

For the simulations conducted with randomly arranged block habitat patterns, the patches exhibit variable sizes, following a distribution with a minimum size determined by the patch-size parameter and a larger maximum size determined by the superposition of several patches (Figures S9 - S11). The overall pattern is analogous to the regular case, with a peak in richness occurring for intermediate patch sizes. However, for values of $\lambda$ higher than 2, the maximum richness is observed at the smaller habitat patch size (Figure S1 & S2). The patches in the random block simulations are generally larger, resulting in lower species richness and diversity, except for the minimum patch size (Figure S7 & S8). Supplementary material (Figures S9 & S32) includes examples of simulations with random block and regular habitat patterns. In these figures, it is evident that for the minimum patch size, only migrants survive in regular habitat patterns with neutral and hierarchical models.

@@

In previous simulation studies, the importance of fragmentation was demonstrated to be pronounced when the habitat amount is low, approximately around 10% [@Hanski2015; @Rybicki2013]. However, experimental studies have observed that with habitat levels around 10-20%, the impact of fragmentation can be positive or show an intermediate maximum [@Loke2019; @With2016]. When habitat amounts are lower (e.g., 7%), the arrangement of patches appears to have no significant effect. Interestingly, our study replicated similar patterns even with a 40% habitat amount. Moreover, other studies employing comparable habitat amounts (32%) also reported higher species richness with increased fragmentation [@Rybicki2020].
